Paper 2, Econ 980x

### 2022-11-28 Paper2.Rmd
comit

---
title: "Paper 2, Econ 980x"
author: "Alice Chen"
date: "2022-11-27"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

```{r regressions, echo=FALSE}

@@

stargazer(g, y, a, title="Various Models", align=TRUE, type = "text")
```

@@

change2

@@

>>>>

---
title: "Paper 2, Econ 980x"
author: "Alice Chen"
date: "2022-11-27"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

```{r regressions}

@@

stargazer(a, b, c, d, title="Various Models", align=TRUE, type = "text")
```

@@

change3 <- newcsv1 %>%
  group_by(gender,  year, new_educ, nchild, marst_simple) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  pivot_wider(values_from = median_bls_leis, names_from = year) %>%
  clean_names() %>%
  mutate(leisure_change = x2009 - x2007)

#child
newcsv1

@@

delta3 <- change3 %>%
  lm(formula = leisure_change ~ gender+ new_educ+ nchild+ marst_simple)
summary(delta3)
